Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-16 paper.qmd
Added bin2 equation with cross reference
Added linked plots video for C-shaped data

$$
b_2 = \Big\lceil1 +\frac{2[r_2 + q(1 + r_2)](b_1 - 1)}{\sqrt{3}(1 + 2q)}\Big\rceil.
$$

@@

The default number of bins $b=b_1\times b_2$ is computed based on the sample size, by setting $b_1=n^{1/3}$, consistent with the Diaconis-Freedman rule [@freedman1981]. The value of $b_2$ is determined analytically by $b_1, q, r_2$ <!-- What is the formula for this? -->. Values of $b_1$ between $2$ and $b_1 = \sqrt{n/r_2}$ are allowed. @fig-param-two-curvy (a) shows the effect of different choices of $b_1$ on the RMSE of the fitted model.

@@

## Reorder the rows of df_b according to the hexID order in df_b_with_center_data
df_b_mnist <- df_b_mnist[match(hexID_mnist, df_b_mnist$hexID),] |>
  dplyr::select(-hexID)

@@

df_exe_mnist <- comb_all_data_model(
  highd_data = training_data_mnist,
  nldr_data = tsne_minst_scaled_temp,
  model_highd = df_bin_mnist,
  model_2d = df_bin_centroids_dens_clust)

>>>>

$$
b_2 = \Big\lceil1 +\frac{2[r_2 + q(1 + r_2)](b_1 - 1)}{\sqrt{3}(1 + 2q)}\Big\rceil.
$${#eq-bin2}

@@

The default number of bins $b=b_1\times b_2$ is computed based on the sample size, by setting $b_1=n^{1/3}$, consistent with the Diaconis-Freedman rule [@freedman1981]. The value of $b_2$ is determined analytically by $b_1, q, r_2$ (@eq-bin2). Values of $b_1$ between $2$ and $b_1 = \sqrt{n/r_2}$ are allowed. @fig-param-two-curvy (a) shows the effect of different choices of $b_1$ on the RMSE of the fitted model.

@@

## Reorder the rows of df_b according to the hexID order in df_b_with_center_data
df_b_mnist <- df_b_mnist[match(hexID_mnist, df_b_mnist$hexID),]

df_b_mnist_temp <- df_b_mnist

df_b_mnist <- df_b_mnist |>
  dplyr::select(-hexID)

@@

df_exe_mnist <- comb_all_data_model(
  highd_data = training_data_mnist,
  nldr_data = tsne_minst_scaled_temp,
  model_highd = df_b_mnist_temp,
  model_2d = df_bin_centroids_dens_clust)
